A game of Competition for Risk

### 2023-05-29 paper/article.tex
Updates from Overleaf

@@

After the failure events are determined, the players that did not fail compare their risk levels, and the player that played the highest risk level is rewarded with a payoff, denoted as $R$. We assume that $R > 0$. In the case of ties between risk levels, we consider several ways of resolving them, such as none of the players receiving the reward, the reward being shared equally between them, or the reward being randomly given to one of them.

@@

\begin{center}
\begin{tabular}{|c|c|c|}
\cline{2-3}
\multicolumn{1}{c|}{} & $f_1\ge r_1$ & $f_1<r_1$ \\
\hline
$f_2\ge r_2$ & $R, 0$ & $-P, R$ \\
\hline
$f_2<r_2$ & $R, -P$ &  $-P, -P$ \\
\hline
\end{tabular}
\end{center}

Each cell contains the rewards to each player. For example, in the upper left cell, no failure happens. Since we assumed $r_1 > r_2$, player 1 gets $R$ and player 2 gets $0$.

@@

We can represent the game described above in the framework of extensive-form games by modeling the drawing of the random variables $f_p$ using Chance nodes. Since the outcomes are subject to randomness, it is natural to assume that the actors operate under the expected utility hypothesis, which implies that they possess a von Neumann–Morgenstern utility function. Consequently, we can define a normal-form game with payoffs equal to the expected payoffs of the corresponding extensive-form game. By doing so, we can leverage the theory of normal-form games and apply various solution concepts, such as Nash equilibria, to analyze the competition between the actors.
\begin{proposition}
The expected utilities $u_p$ are computed as follows in the 2-player game:
\begin{align*}
    u_2(r_1, r_2) &= u_1(r_2, r_1) \text{~(symmetry)}\\
    u_1(r_1, r_2) &= r_2 (1-r_1) R - r_1 P + [ r_1 > r_2 ] (1-r_1)(1-r_2) R
\end{align*}
where $[ \cdot ]$ is the Iverson bracket.
\end{proposition}
\begin{proof}
Player 1 can fail with probability $r_1$, in which case they lose $P$. If Player 2 loses and Player 1 does not, which happens with probability $r_2(1-r_1)$, Player 1 wins $R$. Finally, if none of the players fails, when $r_1 > r_2$, Player 1 can win $R$.
\end{proof}

@@

For finite games, Nash himself proved the existence of mixed Nash equilibria \citep{Nash1950-jp}, while Glicksberg's theorem extended this result to continuous reward functions \citep{Glicksberg1951-wp}. Dasgupta and Maskin \citep{Dasgupta1986-gu} established conditions under which discontinuous games can possess Nash equilibria and symmetric games can admit symmetric equilibria.

@@

\begin{restatable}{theorem}{nashcor}
\label{thm:nashcor}
Up to a set of measure zero, the CfR game admits a unique Nash equilibrium. This equilibrium is symmetric and its distribution is $f(x) = \left[x < 1 - \sqrt{\frac{k - 1}{k + 1}}\right] \frac{ k - 1}{(1-x)^3}$ with $C := \frac{P}{R}$ and $k := \sqrt{(C + 1)^2 + 1}$. The the average move is $\bar r = k - (C+1)$ and the utility of each player is $u^* = R \bar r$.
\end{restatable}

@@

At $C = 1$, the cutoff value is $1 - \sqrt{\frac{\sqrt{5} - 1}{\sqrt{5} + 1}} = 2 - \phi \approx 0.382$ with $\phi$ the Golden ratio. We plot the distribution in Figure \ref{fig:nash}.

@@

\begin{figure}[htbp]
  \centering
  \includesvg[width=0.8\linewidth]{cutoff}
  \caption{The cutoff goes to zero when $C \rightarrow\infty$.}
  \label{fig:cutoff}  
\end{figure}

 The behavior of the cutoff ${r_{max}}$ is displayed in Figure \ref{fig:cutoff}. Unsurprisingly, when $C \rightarrow \infty$, the penalty $P$ becomes much larger than the reward $R$ and the players play closer to $0$.

The case when $C \rightarrow 0$ is more surprising: the maximal cutoff value at $C=0$ is $h = 1 - \sqrt{\frac{\sqrt{2}}{\sqrt{2} + 2}} \approx 0.356$. This is because even if the penalty is $0$, the players cannot get the reward if they ``lose'', which prevents them from taking too much risk. We plot the distribution in Figure \ref{fig:nash}.

@@

\subsection{Nash equilibrium}
Interestingly, our Correlation for Risk game admits an analytical solution even for multiple players. More precisely:
\begin{theorem}\label{thm:multiple}
    There is a unique symmetric Nash equilibrium for in the CfR game with $n$ players defined by $$f(x) = \frac{C + w}{(n-1)(1-x)^{2+\frac{1}{n-1}} (C x + w)^{1 - \frac{1}{n-1}}}$$
    for some constants $r_{max}$ and $w := \bar r ^ {n-1}$ (the probability of winning when taking no risk) such that 
    \begin{align*}
        \int_0^{r_{max}} f(x) dx &= 1 \\
        \int_0^{r_{max}} x f(x) dx &= \bar r 
    \end{align*}
\end{theorem} 
\begin{proof}

@@

$$u(x) = -x P + (1-x) \left( \int_0^x f(y) dy +\int_x^1 y f(y) dy \right)^{n-1} R$$

This equation is quite natural: the player loses $P$ with probability $x$. If they survive, with probability $1-x$, they need the $n-1$ other players to either play a lower value or play a higher value and fail. We can suppose as previously that $0$ is in the support to subtract $u(0)$. We write $\bar r$ for the expectation of the action $r$ under $f$.
$$\left(\frac{\bar r^{n-1} + x C}{1-x} \right)^\frac{1}{n-1} = \int_0^x f(y) dy + \int_x^1 y f(y) dy$$
We define $w := \bar r ^ {n-1}$ to be the probability of winning when taking no risk, we derivate and divide by $1-x$ to obtain:
$$f(x) = \frac{C + w}{(n-1)(1-x)^{2+\frac{1}{n-1}} (C x + w)^{1 - \frac{1}{n-1}}}$$
Finally we can solve $\int_0^{r_{max}} f(x) dx= 1$ and $\int_0^{r_{max}} x f(x) dx = \bar r$. We relegate the description of the numerical estimation of ${r_{max}}$ and $w$ to \ref{estimate}.
\end{proof}

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{solution-multiple-0}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{solution-multiple-1}
  \end{minipage}
  \caption{We observe a clear difference between the cases $C=0$ (no penalty) and $C=1$ (presence of a penalty). In both cases, the cutoff increases. However, the average risk seems to decrease sharply when there is a nonzero penalty with a mode at $r=0$.}
  \label{fig:solution-multiple}  
\end{figure}

@@

We are interested in studying the equilibrium when the number of players goes to infinity. For fixed $C$, we have the following:

\begin{proposition}When $n\rightarrow \infty$,
    $\lim {r_{max}} = \frac{1}{1+C}$ and $\bar r \sim \frac{1}{n C}$
\end{proposition}

@@

\begin{align*}
    \frac{w + n C (1-{r_{max}}) + C {r_{max}}}{n (1-{r_{max}})(C+w)} \sqrt[n-1]{\frac{C{r_{max}}+w}{1-{r_{max}}}} &= 1 + \frac{w + nC}{n(C+w)} \bar r \\
    \sqrt[n-1]{\frac{C{r_{max}}+w}{1-{r_{max}}}} &\rightarrow 1
\end{align*}

@@

\begin{align*}
    \frac{w - nw(1-{r_{max}})+C{r_{max}}}{n(1-{r_{max}})(C+w)} \sqrt[n-1]{\frac{C{r_{max}}+w}{1-{r_{max}}}} &= \bar r \frac{w + nC}{n(C+w)} \\
    \frac{w}{C} + \frac{{r_{max}}}{n(1-{r_{max}})} \sim \frac{{r_{max}}}{n(1-{r_{max}})}  &\sim \bar r
\end{align*}

@@

$\sqrt[n-1]{\frac{C{r_{max}}+w}{1-{r_{max}}}} \rightarrow 1$ implies $\frac{{r_{max}}}{1-{r_{max}}} \rightarrow \frac{1}C$ and ${r_{max}} \rightarrow \frac{1}{1+C}$.\\Finally, $\bar r \sim \frac{1}{nC}$.
\end{proof}

@@

\begin{figure}[htbp]
    \centering
    \includesvg[width=0.8\linewidth]{cutoff-asymptotic}
    \caption{The plot of $r_{max}$ to $\log(C)$ is very similar to the function $\frac{1}{1 + \exp(\cdot)}$. This is because $r_{max} \sim \frac{1}{1+C}$.}
    \label{fig:cutoff-asymptotic}
\end{figure}

@@

We observe that when $C = \frac{1}{n^e}$ with $e \ge 0$, the efficiency $E = n w$ of the Nash equilibrium goes to $0$ if $e \le 1$ and it goes to $1$ if $e > 1$. We plot the behavior of $E$ in Figure \ref{fig:efficiency}.
We interpret this as an indication that resources, here modeled by the ratio $\frac{1}{C} = \frac{R}{P}$ of rewards to penalties, need to scale faster than the number of players for them to adopt an efficient behavior. Scarcity of resources creates an inefficient Nash equilibrium.

@@

    $$p(x) = \frac{1+C}{1-x} \left[x < 1 - \exp\left(-\frac{1}{C+1}\right)\right]$$ 
    We have $$\bar r = 1 - (C+1)\left(1-\exp\left(-\frac{1}{C+1}\right)\right)$$

@@

    $$p(x) = \frac{C}{(1-2x)^{3/2}} \left[x < \frac{1}{2} - \frac{C^2}{2(C+1)^2}\right]$$
    We have  $$\bar r = \frac{1}{2C+2}$$

@@

We present the results of our experiments with different values of $C$, $\tau$, and $\rho$, as well as different numbers of actions, in Figure \ref{fig:linear-shift}, where we plot the maximum distance $d_{max}$ and the parameter $\lambda$ computed according to Section \ref{sec:linear} with \texttt{shift = true}. We also present the results with \texttt{shift = false} in Section \ref{sec:linear-noshift}.

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{linear-dmax-shift}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{linear-lambda-shift}
  \end{minipage}
  \caption{Our experiments with different values of $C$, $\tau$, and $\rho$, as well as different numbers of actions, for the setting with \texttt{shift = true} show that, for almost all values of the parameters, $d_{max}$ is numerically zero. We cross out cases where the solver failed to find a solution, most probably due to rounding errors which caused the small solution set to disappear. In the few cases where $d_{max}$ was not observed to be zero, $\lambda$ is clearly zero, indicating that the best correlated equilibrium is a Nash equilibrium.}
  \label{fig:linear-shift}  
\end{figure}

@@

We implement and evaluate all algorithms to solve a discrete version of our game where the action space is reduced to a grid, with and without a shift. We then report the value of $\textsc{NashConv}$ $\textsc{QuasiNashConv}$ as defined in Section \ref{sec:approx}. We observe on Figure \ref{fig:rm-different} that vanilla Regret Matching outperforms all methods. In general, Regret Matching performs much better than CFR, even when using less actions, using softmax is detrimental, and shifting the action space does not seem to impact performance much. CFR runs faster as it does not involve any random sampling. Therefore, we use vanilla Regret Matching with shifting in the rest of the experiments for the sake of simplicity. Figure \ref{fig:rm-size} shows that the number of sampled actions is the main factor that drives the quality of solutions.

@@

Our results demonstrate that penalties and market frictions have a significant impact on the strategic behavior of actors in competition. Specifically, we find that penalties $C$ decrease both the average risk taken $\bar r$ by the players and their total reward $u$, while market frictions $\tau$ not only decrease the average risk taken but also increase the total reward. We also find that market frictions have a greater impact on the total reward in high-penalty environments. In particular, in particularly inefficient markets with high $\tau$, increasing penalties can improve cooperation and the total reward, as illustrated in Figure \ref{fig:result-noise}.

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{equilibria_rbar_u_tau}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{equilibria_rbar_u_C}
  \end{minipage}
  \caption{
  The two figures depict the relationship between the total reward $u$ and the average risk taken $\bar r$ under different penalty $C$ and market friction $\tau$ settings. The left figure shows constant $C$ level lines, while the right figure shows constant $\tau$ level lines. We observe a linear relationship between $u$ and $\bar r$ when changing $\tau$ at constant $C$. We find that this behavior holds for all values of $\rho$. Interestingly, there seems to exist a linear relationship between $\bar r$ and $u$ when changing $\tau$ for fixed levels of $C$.}
  \label{fig:result-noise}  
\end{figure}

@@

@@

Moreover, the impact of failure penalties (or the absence of a safety net) can exacerbate this dynamic, suggesting that regulators could mitigate perverse incentives by reducing the penalty parameter in a positively correlated environment, such as through bailouts or other protective measures (e.g., deposit insurance, liquidity provision, and bank resolution mechanisms). This perspective aligns with a strand of literature that extrapolates from the Diamond-Dybvig model to inform policy making \citep{bhattacharya1985preference,ennis2009bank}.

Outside of the banking sector, our framework has implications for other policy debates. In the European Union, for instance, the Financial Services Commissioner, Mairead McGuinness, recently proposed banning ``inducements'' – commissions paid by banks or insurers to financial advisors who sell their products. Proponents argue this would enhance transparency and reduce costs. Critics, however, fear it could inhibit access to financial advice. Within our model, increasing transparency equates to reducing the friction parameter $\tau$, which alters the equilibrium, potentially heightening risk for financial institutions but also augmenting returns for consumers. Our findings indicate that regulators might safeguard consumers and influence prices simply by mandating transparency. However, we caution that the impact of such a policy on market frictions is uncertain, as it could inadvertently limit access to information via advisors.

Furthermore, in France, a legislative proposal by MPs Husson and Montgolfier seeks to enhance the transferability of contracts between life insurers, effectively reducing market frictions. Our framework suggests that, in response, insurers could take on more risk due to increased competition. However, the relationship between risk and interest rates may also change, as performance becomes costlier in terms of risk when the duration of contracts decreases because of enhanced transferability. Consequently, while our model predicts an uptick in the risks assumed by insurers, the ultimate benefit to savers remains ambiguous.

@@

We derivate to obtain:
$$f(a) = \left(\bar b + \frac{P}{R}\right) \frac{1}{(1-a)^3}$$
We now have two unknowns and two unknowns:
$$
\left\{ \begin{array}{ll}
h := \sup S  \text{ such that } \int_0^h f(x) dx = 1\\
\bar b = \int_0^h x f(x) dx
\end{array} \right.
$$
We define $C := \frac{P}{R}$.\\
$$\int_0^h f(x) dx = \frac{\bar b + C}{2} \left(\frac{1}{(h-1)^2}-1\right) = 1$$\\
$$\int_0^h x f(x) dx = \bar b = \frac{\bar b + C}{2} \frac{h^2}{(h-1)^2}$$

We get
$$\bar b = \frac{h^2}{1-(h-1)^2}$$
$$2 \frac{(h-1)^2}{1 - (h-1)^2} - C = \frac{h^2}{1 - (h-1)^2}$$
$$2(h-1)^2 - C + C (h-1)^2 - h^2 = 0$$
$$(C + 1) h^2 - (2 C + 4) h + 2 = 0$$
Hence, $h = \frac{2 + C \pm \sqrt{C^2 + 2 C + 2}}{1 + C}$\\
Since $h<1$, we get
\begin{align*}
    h &= \frac{2 + C - \sqrt{C^2 + 2 C + 2}}{1 + C}\\
      &= 1 - \frac{\sqrt{(C + 1)^2 + 1} - 1}{1+C}
\end{align*}
We remark that $(\sqrt{(C + 1)^2 + 1} + 1)( \sqrt{(C + 1)^2 + 1} - 1) = (C+1)^2$\\
Hence $h = 1 - \sqrt{\frac{\sqrt{(C + 1)^2 + 1} - 1}{\sqrt{(C + 1)^2 + 1} + 1}}$
\begin{align*}\bar b + C &=\frac{2}{\frac{1}{(h-1)^2} - 1}\\
&= \frac{2}{\frac{\sqrt{(C + 1)^2 + 1} + 1}{\sqrt{(C + 1)^2 + 1} - 1} - 1}\\
&= \sqrt{(C + 1)^2 + 1} - 1\end{align*}
Finally, $f(x) = \left[x < 1 - \sqrt{\frac{k - 1}{k + 1}}\right] \frac{ k - 1}{(1-x)^3}$ with $k := \sqrt{(C + 1)^2 + 1}$\\
From the expressions above, we get $\bar b = k - 1 - C$ and $u^* = R \bar b$.
\end{proof}

@@

$$f(x) = \frac{C + w}{(n-1)(1-x)^{2+\frac{1}{n-1}} (C x + w)^{1 - \frac{1}{n-1}}}$$
\begin{align*}
        \int_0^{r_{max}} f(x) dx &= 1 \\
        \int_0^{r_{max}} x f(x) dx &= \bar r 
\end{align*}
with $$w := \bar r ^ {n-1}$$

>>>>

%% break url
\usepackage{xurl}

@@

After the failure events are determined, the players that did not fail compare their risk levels, and the player that played the highest risk level is rewarded with a payoff, denoted as $R$. Since the game is unchanged when scaling both $P$ and $R$, we assume $R = 1$. In the case of ties between risk levels, we consider several ways of resolving them, such as none of the players receiving the reward, the reward being shared equally between them, or the reward being randomly given to one of them.

@@

\begin{center}
\begin{tabular}{|c|c|c|}
\cline{2-3}
\multicolumn{1}{c|}{} & $f_1\ge r_1$ & $f_1<r_1$ \\
\hline
$f_2\ge r_2$ & $R=1, 0$ & $-P, 1$ \\
\hline
$f_2<r_2$ & $1, -P$ &  $-P, -P$ \\
\hline
\end{tabular}
\end{center}

Each cell contains the rewards to each player. For example, in the upper left cell, no failure happens. Since we assumed $r_1 > r_2$, player 1 gets $R=1$ and player 2 gets $0$.

@@

We can represent the game described above in the framework of extensive-form games\citep{hart1992games} by modeling the drawing of the random variables $f_p$ using Chance nodes. Since the outcomes are subject to randomness, it is natural to assume that the actors operate under the expected utility hypothesis, which implies that they possess a von Neumann–Morgenstern utility function\citep{neumann1944theory}. Consequently, we can define a normal-form game with payoffs equal to the expected payoffs of the corresponding extensive-form game. By doing so, we can leverage the theory of normal-form games and apply various solution concepts, such as Nash equilibria, to analyze the competition between the actors.
\begin{proposition}
The expected utilities $u_p$ are computed as follows in the 2-player game:
\begin{align*}
    u_2(r_1, r_2) &= u_1(r_2, r_1) \text{~(symmetry)}\\
    u_1(r_1, r_2) &= r_2 (1-r_1) R - r_1 P + [ r_1 > r_2 ] (1-r_1)(1-r_2) R
\end{align*}
where $[ \cdot ]$ is the Iverson bracket.
\end{proposition}
\begin{proof}
Player 1 can fail with probability $r_1$, in which case they lose $P$. If Player 2 loses and Player 1 does not, which happens with probability $r_2(1-r_1)$, Player 1 wins $R$. Finally, if none of the players fails, when $r_1 > r_2$, Player 1 can win $R$.
\end{proof}

@@

For finite games, \citet{Nash1950-jp} proved the existence of mixed Nash equilibria, while Glicksberg's theorem \citep{Glicksberg1951-wp} extended  this result to continuous reward functions. \citet{Dasgupta1986-gu} established conditions under which discontinuous games can possess Nash equilibria and symmetric games can admit symmetric equilibria.

@@

\begin{restatable}{theorem}{nashcor}
\label{thm:nashcor}
Up to a set of measure zero, the CfR game admits a unique Nash equilibrium. This equilibrium is symmetric and its distribution is $f(x) = \left[x < 1 - \sqrt{\frac{k - 1}{k + 1}}\right] \frac{ k - 1}{(1-x)^3}$ with $k := \sqrt{(P + 1)^2 + 1}$. The the average move is $\bar r = k - (P+1)$ and the utility of each player is $u^* = \bar r$.
\end{restatable}

@@

At $P = 1$, the cutoff value is $1 - \sqrt{\frac{\sqrt{5} - 1}{\sqrt{5} + 1}} = 2 - \phi \approx 0.382$ with $\phi$ the Golden ratio. We plot the distribution in Figure \ref{fig:nash}.

@@

\begin{figure}[htbp]
  \centering
  \includesvg[width=0.8\linewidth]{cutoff}
  \caption{The cutoff goes to zero when $P \rightarrow\infty$.}
  \label{fig:cutoff}  
\end{figure}

 The behavior of the cutoff ${r_{max}}$ is displayed in Figure \ref{fig:cutoff}. Unsurprisingly, when $P \rightarrow \infty$, the penalty becomes much larger than the reward and the players play closer to $0$.

The case when $P \rightarrow 0$ is more surprising: the maximal cutoff value at $P=0$ is $h = 1 - \sqrt{\frac{\sqrt{2}}{\sqrt{2} + 2}} \approx 0.356$. This is because even if the penalty is $0$, the players cannot get the reward if they ``lose'', which prevents them from taking too much risk. We plot the distribution in Figure \ref{fig:nash}.

@@

\subsection{Nash equilibrium}
Interestingly, our Correlation for Risk game admits an analytical solution even for multiple players. More precisely:
\begin{theorem}\label{thm:multiple}
    There is a unique symmetric Nash equilibrium for in the CfR game with $n$ players defined by $$f(x) = \frac{P + w}{(n-1)(1-x)^{2+\frac{1}{n-1}} (P x + w)^{1 - \frac{1}{n-1}}}$$
    for some constants $r_{max}$ and $w := \bar r ^ {n-1}$ (the probability of winning when taking no risk) such that 
    \begin{align*}
        \int_0^{r_{max}} f(x) dx &= 1 \\
        \int_0^{r_{max}} x f(x) dx &= \bar r 
    \end{align*}
\end{theorem} 
\begin{proof}

@@

$$u(x) = -x P + (1-x) \left( \int_0^x f(y) dy +\int_x^1 y f(y) dy \right)^{n-1}$$

This equation is quite natural: the player loses $P$ with probability $x$. If they survive, with probability $1-x$, they need the $n-1$ other players to either play a lower value or play a higher value and fail. We can suppose as previously that $0$ is in the support to subtract $u(0)$. We write $\bar r$ for the expectation of the action $r$ under $f$.
$$\left(\frac{\bar r^{n-1} + x P}{1-x} \right)^\frac{1}{n-1} = \int_0^x f(y) dy + \int_x^1 y f(y) dy$$
We define $w := \bar r ^ {n-1}$ to be the probability of winning when taking no risk, we derivate and divide by $1-x$ to obtain:
$$f(x) = \frac{P + w}{(n-1)(1-x)^{2+\frac{1}{n-1}} (P x + w)^{1 - \frac{1}{n-1}}}$$
Finally we can solve $\int_0^{r_{max}} f(x) dx= 1$ and $\int_0^{r_{max}} x f(x) dx = \bar r$. We relegate the description of the numerical estimation of ${r_{max}}$ and $w$ to \ref{estimate}.
\end{proof}

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{solution-multiple-0}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{solution-multiple-1}
  \end{minipage}
  \caption{We observe a clear difference between the cases $P=0$ (no penalty) and $P=1$ (presence of a penalty). In both cases, the cutoff increases. However, the average risk seems to decrease sharply when there is a nonzero penalty with a mode at $r=0$.}
  \label{fig:solution-multiple}  
\end{figure}

@@

We are interested in studying the equilibrium when the number of players goes to infinity. For fixed $P$, we have the following:

\begin{proposition}When $n\rightarrow \infty$,
    $\lim {r_{max}} = \frac{1}{1+P}$ and $\bar r \sim \frac{1}{n P}$
\end{proposition}

@@

\begin{align*}
    \frac{w + n P (1-{r_{max}}) + P {r_{max}}}{n (1-{r_{max}})(P+w)} \sqrt[n-1]{\frac{P{r_{max}}+w}{1-{r_{max}}}} &= 1 + \frac{w + nP}{n(P+w)} \bar r \\
    \sqrt[n-1]{\frac{P{r_{max}}+w}{1-{r_{max}}}} &\rightarrow 1
\end{align*}

@@

\begin{align*}
    \frac{w - nw(1-{r_{max}})+P{r_{max}}}{n(1-{r_{max}})(P+w)} \sqrt[n-1]{\frac{P{r_{max}}+w}{1-{r_{max}}}} &= \bar r \frac{w + nP}{n(P+w)} \\
    \frac{w}{P} + \frac{{r_{max}}}{n(1-{r_{max}})} \sim \frac{{r_{max}}}{n(1-{r_{max}})}  &\sim \bar r
\end{align*}

@@

$\sqrt[n-1]{\frac{P{r_{max}}+w}{1-{r_{max}}}} \rightarrow 1$ implies $\frac{{r_{max}}}{1-{r_{max}}} \rightarrow \frac{1}P$ and ${r_{max}} \rightarrow \frac{1}{1+P}$.\\Finally, $\bar r \sim \frac{1}{nP}$.
\end{proof}

@@

\begin{figure}[htbp]
    \centering
    \includesvg[width=0.8\linewidth]{cutoff-asymptotic}
    \caption{The plot of $r_{max}$ to $\log(P)$ is very similar to the function $\frac{1}{1 + \exp(\cdot)}$. This is because $r_{max} \sim \frac{1}{1+P}$.}
    \label{fig:cutoff-asymptotic}
\end{figure}

@@

We observe that when $P = \frac{1}{n^e}$ with $e \ge 0$, the efficiency $E = n w$ of the Nash equilibrium goes to $0$ if $e \le 1$ and it goes to $1$ if $e > 1$. We plot the behavior of $E$ in Figure \ref{fig:efficiency}.
We interpret this as an indication that resources, here modeled by the ratio $\frac{1}{P} = \frac{R}{P}$ of rewards to penalties, need to scale faster than the number of players for them to adopt an efficient behavior. Scarcity of resources creates an inefficient Nash equilibrium.

@@

    $$p(x) = \frac{1+P}{1-x} \left[x < 1 - \exp\left(-\frac{1}{P+1}\right)\right]$$ 
    We have $$\bar r = 1 - (P+1)\left(1-\exp\left(-\frac{1}{P+1}\right)\right)$$

@@

    $$p(x) = \frac{P}{(1-2x)^{3/2}} \left[x < \frac{1}{2} - \frac{P^2}{2(P+1)^2}\right]$$
    We have  $$\bar r = \frac{1}{2P+2}$$

@@

We present the results of our experiments with different values of $P$, $\tau$, and $\rho$, as well as different numbers of actions, in Figure \ref{fig:linear-shift}, where we plot the maximum distance $d_{max}$ and the parameter $\lambda$ computed according to Section \ref{sec:linear} with \texttt{shift = true}. We also present the results with \texttt{shift = false} in Section \ref{sec:linear-noshift}.

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{linear-dmax-shift}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{linear-lambda-shift}
  \end{minipage}
  \caption{Our experiments with different values of $P$, $\tau$, and $\rho$, as well as different numbers of actions, for the setting with \texttt{shift = true} show that, for almost all values of the parameters, $d_{max}$ is numerically zero. We cross out cases where the solver failed to find a solution, most probably due to rounding errors which caused the small solution set to disappear. In the few cases where $d_{max}$ was not observed to be zero, $\lambda$ is clearly zero, indicating that the best correlated equilibrium is a Nash equilibrium.}
  \label{fig:linear-shift}  
\end{figure}

@@

We implement and evaluate all algorithms to solve a discrete version of our game where the action space is reduced to a grid, with and without a shift. We then report the value of $\textsc{NashConv}$ $\textsc{QuasiNashConv}$ as defined in Section \ref{sec:approx}. We display the solution found by Regret Matching in Figure \ref{fig:rm-sol} and check that it matches the actual solution from Figure \ref{fig:nash}. We observe on Figure \ref{fig:rm-different} that vanilla Regret Matching outperforms all methods. In general, Regret Matching performs much better than CFR, even when using less actions, using softmax is detrimental, and shifting the action space does not seem to impact performance much. CFR runs faster as it does not involve any random sampling. Therefore, we use vanilla Regret Matching with shifting in the rest of the experiments for the sake of simplicity. Figure \ref{fig:rm-size} shows that the number of sampled actions is the main factor that drives the quality of solutions.

\begin{figure}[htbp]
  \centering
  \includesvg[width=0.8\linewidth]{rm-sol}
  \caption{}
  \label{fig:rm-sol}  
\end{figure}

@@

Our results demonstrate that penalties and market frictions have a significant impact on the strategic behavior of actors in competition. Specifically, we find that penalties $P$ decrease both the average risk taken $\bar r$ by the players and their total reward $u$, while market frictions $\tau$ not only decrease the average risk taken but also increase the total reward. We also find that market frictions have a greater impact on the total reward in high-penalty environments. In particular, in particularly inefficient markets with high $\tau$, increasing penalties can improve cooperation and the total reward, as illustrated in Figure \ref{fig:result-noise}.

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{equilibria_rbar_u_tau}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{equilibria_rbar_u_C}
  \end{minipage}
  \caption{
  The two figures depict the relationship between the total reward $u$ and the average risk taken $\bar r$ under different penalty $P$ and market friction $\tau$ settings. The left figure shows constant $P$ level lines, while the right figure shows constant $\tau$ level lines. We observe a linear relationship between $u$ and $\bar r$ when changing $\tau$ at constant $P$. We find that this behavior holds for all values of $\rho$. Interestingly, there seems to exist a linear relationship between $\bar r$ and $u$ when changing $\tau$ for fixed levels of $P$.}
  \label{fig:result-noise}  
\end{figure}

@@

\subsection{Ties with the Diamond-Dybvig model}

@@

Moreover, the impact of failure penalties (or the absence of a safety net) can exacerbate this dynamic, suggesting that regulators could mitigate perverse incentives by reducing the penalty parameter $P$ in a positively correlated environment, such as through bailouts or other protective measures (e.g., deposit insurance, liquidity provision, and bank resolution mechanisms). This perspective aligns with a strand of literature that extrapolates from the Diamond-Dybvig model to inform policy making \citep{bhattacharya1985preference,ennis2009bank}.

\subsection{Practical applications in current policy debates}

Outside of the banking sector, our framework has implications for other policy debates. In the European Union, for instance, the Financial Services Commissioner, Mairead McGuinness, recently proposed banning ``inducements'' – commissions paid by banks or insurers to financial advisors who sell their products \citep{Jones2023}. Proponents argue this would enhance transparency and reduce costs. Critics, however, fear it could inhibit access to financial advice. Within our model, increasing transparency equates to reducing the friction parameter $\tau$, which alters the equilibrium, potentially heightening risk for financial institutions but also augmenting returns for consumers. Our findings indicate that regulators might safeguard consumers and influence prices simply by mandating transparency. However, we caution that the impact of such a policy on market frictions is uncertain, as it could inadvertently limit access to information via advisors.

Furthermore, in France, a legislative proposal by MPs Husson and Montgolfier \citep{senat2023} seeks to enhance the transferability of contracts between life insurers, effectively reducing market frictions. Our framework suggests that, in response, insurers could take on more risk due to increased competition. However, the relationship between risk and interest rates may also change, as performance becomes costlier in terms of risk when the duration of contracts decreases because of enhanced transferability. Consequently, while our model predicts an uptick in the risks assumed by insurers, the ultimate benefit to savers remains ambiguous.

@@

We derivate to obtain:
$$f(a) = \left(\bar b + \frac{P}{R}\right) \frac{1}{(1-a)^3}$$
We now have two unknowns and two unknowns:
$$
\left\{ \begin{array}{ll}
h := \sup S  \text{ such that } \int_0^h f(x) dx = 1\\
\bar b = \int_0^h x f(x) dx
\end{array} \right.
$$
We define $P := \frac{P}{R}$.\\
$$\int_0^h f(x) dx = \frac{\bar b + P}{2} \left(\frac{1}{(h-1)^2}-1\right) = 1$$\\
$$\int_0^h x f(x) dx = \bar b = \frac{\bar b + P}{2} \frac{h^2}{(h-1)^2}$$

We get
$$\bar b = \frac{h^2}{1-(h-1)^2}$$
$$2 \frac{(h-1)^2}{1 - (h-1)^2} - P = \frac{h^2}{1 - (h-1)^2}$$
$$2(h-1)^2 - P + P(h-1)^2 - h^2 = 0$$
$$(P+ 1) h^2 - (2 P+ 4) h + 2 = 0$$
Hence, $h = \frac{2 + P\pm \sqrt{P^2 + 2 P+ 2}}{1 + P}$\\
Since $h<1$, we get
\begin{align*}
    h &= \frac{2 + P- \sqrt{P^2 + 2 P+ 2}}{1 + P}\\
      &= 1 - \frac{\sqrt{(P+ 1)^2 + 1} - 1}{1+P}
\end{align*}
We remark that $(\sqrt{(P+ 1)^2 + 1} + 1)( \sqrt{(P+ 1)^2 + 1} - 1) = (P+1)^2$\\
Hence $h = 1 - \sqrt{\frac{\sqrt{(P+ 1)^2 + 1} - 1}{\sqrt{(P+ 1)^2 + 1} + 1}}$
\begin{align*}\bar b + P&=\frac{2}{\frac{1}{(h-1)^2} - 1}\\
&= \frac{2}{\frac{\sqrt{(P+ 1)^2 + 1} + 1}{\sqrt{(P+ 1)^2 + 1} - 1} - 1}\\
&= \sqrt{(P+ 1)^2 + 1} - 1\end{align*}
Finally, $f(x) = \left[x < 1 - \sqrt{\frac{k - 1}{k + 1}}\right] \frac{ k - 1}{(1-x)^3}$ with $k := \sqrt{(P+ 1)^2 + 1}$\\
From the expressions above, we get $\bar b = k - 1 - P$ and $u^* = R \bar b$.
\end{proof}

@@

$$f(x) = \frac{P+ w}{(n-1)(1-x)^{2+\frac{1}{n-1}} (Px + w)^{1 - \frac{1}{n-1}}}$$
\begin{align*}
        \int_0^{r_{max}} f(x) dx &= 1 \\
        \int_0^{r_{max}} x f(x) dx &= \bar r 
\end{align*}
with $$w := \bar r ^ {n-1}$$
